### 2017-08-24 Sections/about_the_authors.tex
Cost vector analysis

\documentclass[aps,prl,twocolumn,amsmath,amssymb,nofootinbib,superscriptaddress]{revtex4}

\newcommand{\bra}[1]{\langle#1|}
\newcommand{\ket}[1]{|#1\rangle}
\newcommand{\op}[2]{\hat{\textbf{#1}}_{#2}}
\newcommand{\dagop}[2]{\hat{\textbf{#1}}_{#2}^\dag}
\usepackage[pdftex]{graphicx}
\usepackage{mathrsfs}
\usepackage[colorlinks]{hyperref}
\usepackage{graphbox}
\usepackage{wrapfig}

\begin{document}

@@

Peter Rohde is an ARC Future Fellow in the Centre for Quantum Software \& Information at the University of Technology Sydney. He obtained his PhD in theoretical physics at the University of Queensland. He has worked at highly-acclaimed international institutes, including the University of Oxford and the Max-Planck Institute. His theoretical proposals have inspired several leading experimental efforts. In his spare time he is a musician, composer, public speaker, adrenaline junkie, and charity worker. He is a very naughty boy and was expelled from preschool.

@@

@@

Jon Dowling is Professor and Hearne Chair of Theoretical Physics, and Co-Director of the Hearne Institute for Theoretical Physics at Louisiana State University. He has a highly-acclaimed research career, and is author of the popular book \textit{Schr\"odinger's Killer App: Race to Build the World's First Quantum Computer}.

@@

Bill Munro obtained his PhD at the University of Waikato, and has since held numerous prestigious fellowships and appointments. He currently works at NTT Japan, where he is Senior Research Scientist and leader of the theoretical quantum physics research group.

\end{document}

>>>>

%
% About the Authors
%

\section*{About the authors}

@@

Peter Rohde is an ARC Future Fellow in the Centre for Quantum Software \& Information at the University of Technology Sydney (UTS:QSI), and associate member of the Hearne Institute for Theoretical Physics at Louisiana State University. He obtained a Bachelor of Computer Systems Engineering with First Class Honours, and a PhD in theoretical physics at the University of Queensland. He has worked at highly-acclaimed international institutes, including the University of Oxford, University of Queensland, Institute for Molecular Biosciences and Max-Planck Institute for the Science of Light, with over 45 publications and 1,100 citations in quantum optics, quantum computing, quantum information theory and ecology. His theoretical proposals have inspired several leading experimental efforts, including time-bin encoded boson-sampling and sub-shot-noise limited quantum metrology. In his spare time he is a musician, composer, public speaker, charity worker, mountaineer and adrenaline junkie. He regularly speaks at prominent scientific outreach events, features in newspaper and magazine articles, and conducts radio interviews. He is a very naughty boy and was expelled from preschool.

@@

\comment{Complete this section}

@@

Jon Dowling is Professor and Hearne Chair of Theoretical Physics, and Co-Director of the Hearne Institute for Theoretical Physics at Louisiana State University. He has a highly-acclaimed research career, with over 450 publications and 15,000 citations. He is author of the popular book \textit{Schr\"odinger's Killer App: Race to Build the World's First Quantum Computer}.

\comment{Complete this section}

@@

Bill Munro obtained his PhD at the University of Waikato, and has since held numerous prestigious fellowships and positions. He is currently Senior Research Scientist and leader of the theoretical quantum physics research group at NTT Japan.

\comment{Complete this section}
